---
title: "100-sequenced-samples"
author: "Mac Campbell"
date: "November 6, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

## Organizing
Location, data type, meta (life history profile, sex, etc.) of fish

```{r}
library(tidyverse)
```

```{r}
d<-read_csv("sequenced-fish/samples-barcodes-12162021.csv")
```

want:
id      seq     style
D708_508        TAATGCGC-GTACTGAC       TruSeq
D709_501        CGGCTATG-TATAGCCT       TruSeq
D709_502        CGGCTATG-ATAGAGGC       TruSeq


```{r}
d15<-d %>% filter(`library number`=="SOMM515") %>% separate(`i7 primer name`, into =c("Type","i7Well"), 
                                                            remove=FALSE)
barcodes<-read_tsv("demultiplex/sbf1-barcodes.txt")
d15<-left_join(d15, barcodes)

b15<-read_tsv("demultiplex/top15", col_names = "Combo") %>% separate(Combo, into=c("Hits","Sbfi7","i5act"), 
                                                                     remove=FALSE)

c15<-d15 %>% left_join(b15) %>% mutate(BarcodeActual=paste0(Sbfi7,"-",i5act))

write_csv(c15, "sequenced-fish/SOMM515.csv")

somm515<-c15 %>% select(`Sample name`, BarcodeActual)
write_tsv(somm515, "demultiplex/somm515.tsv", col_names = FALSE)

```

```{r, eval=FALSE}
names<-c15 %>% separate(`i5 primer Name`, into = c("Color","i5Well","i5F")) %>% select(i7Well, Sbfi7,i5Well, i5act, BarcodeActual,Hits) %>% arrange(i7Well) 

write_csv(names, file="demultiplex/barcodes.csv")

```

Trying.    
```{sh, eval=FALSE}
$HOME/bin/fastq-multx -B demultiplex/somm515.tsv \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM515/SOMM515_S1_L001_I1_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM515/SOMM515_S1_L001_I2_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM515/SOMM515_S1_L001_R1_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM515/SOMM515_S1_L001_R2_001.fastq.gz \
-o n/a -o n/a \
-o /share/schreierlab/smelt-wgs/demulti-SOMM515/%_R1.fastq \
-o /share/schreierlab/smelt-wgs/demulti-SOMM515/%_R2.fastq
```

Works!!!!


```{r}
d17<-d %>% filter(`library number`=="SOMM517") %>% separate(`i7 primer name`, into =c("Type","i7Well"), 
                                                            remove=FALSE)
barcodes<-read_tsv("demultiplex/sbf1-barcodes.txt")
d17<-left_join(d17, barcodes)

b17<-read_tsv("demultiplex/top17", col_names = "Combo") %>% separate(Combo, into=c("Hits","Sbfi7","i5act"), 
                                                                     remove=FALSE)

c17<-d17 %>% left_join(b17) %>% mutate(BarcodeActual=paste0(Sbfi7,"-",i5act))

write_csv(c17, "sequenced-fish/SOMM517.csv")

somm517<-c17 %>% select(`Sample name`, BarcodeActual)
write_tsv(somm517, "demultiplex/somm517.tsv", col_names = FALSE)

```

```{r, eval=FALSE}
names17<-c17 %>% separate(`i5 primer Name`, into = c("Color","i5Well","i5F")) %>% select(i7Well, Sbfi7,i5Well, i5act, BarcodeActual,Hits) %>% arrange(i7Well) 

write_csv(names17, file="demultiplex/barcodes17.csv")

```

```{r}
n15<-read_csv("demultiplex/barcodes.csv")
n17<-read_csv("demultiplex/barcodes17.csv")

total<-bind_rows(n15, n17)
```


```{sh,eval=FALSE}
$HOME/bin/fastq-multx -B demultiplex/somm517.tsv \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM517/SOMM517_S1_L003_I1_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM517/SOMM517_S1_L003_I2_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM517/SOMM517_S1_L003_R1_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM517/SOMM517_S1_L003_R2_001.fastq.gz \
-o n/a -o n/a \
-o /share/schreierlab/smelt-wgs/demulti-SOMM517/%_R1.fastq \
-o /share/schreierlab/smelt-wgs/demulti-SOMM517/%_R2.fastq
```

Run like:   
```{sh, eval=FALSE}
fastq-multx -B barcodes.tsv -m 0 \
    Undetermined_S0_L001_I1_001.fastq.gz \
    Undetermined_S0_L001_I2_001.fastq.gz \
    Undetermined_S0_L001_R1_001.fastq.gz \
    Undetermined_S0_L001_R2_001.fastq.gz \
    -o n/a -o n/a -o %_R1.fastq -o %_R2.fastq
```

Testing:
barcodes.txt looks like:
Sample-1 AGGCAC-TGCAGGTA TruSeq
Sample-2 GCGCCC-CATGGCTA TruSeq
Sample-3 CGTCTT-GGCATACT TruSeq
Sample-4 TCAGTT-ACAGCTCA TruSeq
Sample-5 GACCCT-GCGTCATT TruSeq
      
```{sh,eval=FAlSE}
$HOME/bin/fastq-multx -B data/barcodes.txt \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM515/SOMM515_S1_L001_I1_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM515/SOMM515_S1_L001_I2_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM515/SOMM515_S1_L001_R1_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM515/SOMM515_S1_L001_R2_001.fastq.gz \
-o n/a -o n/a \
-o /share/schreierlab/smelt-wgs/demulti-SOMM515/%_R1.fastq \
-o /share/schreierlab/smelt-wgs/demulti-SOMM515/%_R2.fastq
```

this works....

But the barcodes provided by Sean don't.     
12/17/2021 needs resolution.     

```{sh, eval=FALSE}
module load fastq-multx 
srun -p production -t 1-01:00:0 fastq-multx -B demultiplex/somm515.tsv \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM515/SOMM515_S1_L001_I1_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM515/SOMM515_S1_L001_I2_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM515/SOMM515_S1_L001_R1_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM515/SOMM515_S1_L001_R2_001.fastq.gz \
-o n/a -o n/a \
-o /share/schreierlab/smelt-wgs/demulti-SOMM515/%_R1.fastq \
-o /share/schreierlab/smelt-wgs/demulti-SOMM515/%_R2.fastq
```


```{sh,eval=FALSE}
srun -p production -t 1-01:00:0 fastq-multx -B demultiplex/somm516.tsv \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM516/SOMM516_S1_L001_I1_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM516/SOMM516_S1_L001_I2_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM516/SOMM516_S1_L001_R1_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM516/SOMM516_S1_L001_R2_001.fastq.gz \
-o n/a -o n/a \
-o /share/schreierlab/smelt-wgs/demulti-SOMM516/%_R1.fastq \
-o /share/schreierlab/smelt-wgs/demulti-SOMM516/%_R2.fastq
```



```{sh,eval=FALSE}
srun -p production -t 1-01:00:0 fastq-multx -B demultiplex/somm517.tsv \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM517/SOMM517_S1_L001_I1_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM517/SOMM517_S1_L001_I2_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM517/SOMM517_S1_L001_R1_001.fastq.gz \
/share/schreierlab/smelt-wgs/Project_AFSR_SOMM517/SOMM517_S1_L001_R2_001.fastq.gz \
-o n/a -o n/a \
-o /share/schreierlab/smelt-wgs/demulti-SOMM517/%_R1.fastq \
-o /share/schreierlab/smelt-wgs/demulti-SOMM517/%_R2.fastq
```
