---
title: "1202-sanity-check"
output: html_document
date: "2023-04-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message = FALSE)
```


```{r}
library(tidyverse)
library(DESeq2)
library(apeglm)
```

## Test Data

```{r}
cts <- as.matrix(read.csv("outputs/1200/pasilla_gene_counts.tsv",sep="\t",row.names="gene_id"))

coldata <- read.csv("outputs/1200/coldata.tsv",sep="\t", row.names=1)

dds <- DESeqDataSetFromMatrix(countData = cts,
                              colData = coldata,
                              design = ~ Category)
dds
```

```{r}
keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]
```

```{r}
dds <- DESeq(dds)
res <- results(dds)
res
```

```{r}
resOrdered <- res[order(res$pvalue),]
results<-as_tibble(resOrdered)
results$Gene<-rownames(resOrdered)
results<-results %>% relocate(Gene) %>% filter(padj<0.05, abs(log2FoldChange) >= 1)
results
```

```{r}
vsd <- vst(dds, blind=FALSE)
ntd <- normTransform(dds)
```

```{r}
pcaData <- plotPCA(vsd, intgroup=c("Category"), returnData=TRUE) %>% 
  left_join(sum, by=c("name"="Sample"))
percentVar <- round(100 * attr(pcaData, "percentVar"))


pca<-ggplot(pcaData, aes(PC1, PC2, fill=Category, shape=Category)) +
  geom_point(size=3, alpha=0.9) +
#  geom_text_repel(data=pcaData, aes(x=PC1, y=PC2, fill=Type, label=name)) +
  xlab(paste0("PC1: ",percentVar[1],"% variance")) +
  ylab(paste0("PC2: ",percentVar[2],"% variance")) + 
  coord_fixed() +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  scale_shape_manual(values=c(21,24)) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  scale_fill_viridis_d()

pca
```

Yeah, again, biggest variance not according to hdi/ldi category

```{r}
df<-t(assay(vsd)) %>% as_tibble()
df$Sample<-colnames(vsd)
df$Condition<-vsd$Category
df<-relocate(df,Sample, Condition)
```

```{r}
ddf<-df %>% pivot_longer(cols=3:18558, names_to = c("Gene"), values_to = c("Count"))
ddf
```



```{r}
ggplot(ddf) +
  geom_boxplot(aes(x=Sample, y=Count)) +
  theme(axis.text.x = element_text(angle=45, hjust=1)) +
  facet_grid(.~Condition, scales = "free_x") +
  theme_bw()

```

```{r}
des<-filter(ddf, Gene %in% results$Gene)
sub<-results %>% arrange(-abs(log2FoldChange)) %>% head(n=20)
des<-filter(ddf, Gene %in% sub$Gene)
des <- des %>% left_join(results)

d2 <- des %>% mutate(FoldChange=ifelse(log2FoldChange < 0, "Negative","Positive"))
d2$Sample<-factor(d2$Sample, levels = unique(ddf$Sample))
ggplot() +
  geom_line(data=d2, aes(x=Sample, y=Count, group=Gene, color=FoldChange), alpha=0.5) +
  facet_grid(FoldChange ~ ., scales="free_x") +
  theme(axis.text.x = element_text(angle=45, vjust=0.5)) +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  scale_colour_viridis_d(option="turbo")

```

For all the data.



```{r}
load("outputs/1201/dds.rda")
load("outputs/1201/res")
```


```{r}
cts <- as.matrix(read.csv("outputs/1201/highs.tsv",sep="\t",row.names="gene_id"))
```

```{r}
coldata <- read.csv("outputs/1201/coldata-highs.tsv",sep="\t", row.names=1)
coldata
```

```{r}
dds <- DESeqDataSetFromMatrix(countData = cts,
                              colData = coldata,
                              design = ~ Type)
dds

```

```{r}
#keep <- rowSums(counts(dds)) >= 10
X<-30
keep<-rowSums(counts(dds) >= 10) >= X

dds <- dds[keep,]
```


Make PCA
```{r}
vsd <- vst(dds, blind=FALSE)
```

```{r}
pcaData <- plotPCA(vsd, intgroup=c("Type"), returnData=TRUE)
percentVar <- round(100 * attr(pcaData, "percentVar"))


pca<-ggplot(pcaData, aes(PC1, PC2, fill=Type, shape=Type)) +
  geom_point(size=3, alpha=0.9) +
#  geom_text_repel(data=pcaData, aes(x=PC1, y=PC2, fill=Type, label=name)) +
  xlab(paste0("PC1: ",percentVar[1],"% variance")) +
  ylab(paste0("PC2: ",percentVar[2],"% variance")) + 
  coord_fixed() +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  scale_shape_manual(values=c(21,24)) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  scale_fill_viridis_d()

pca
```


```{r}
dds <- DESeq(dds)
res <- results(dds)
res
```

```{r}
resOrdered <- res[order(res$pvalue),]
```

```{r}
summary(res)
```

```{r}
resOrdered <- res[order(res$pvalue),]
results<-as_tibble(resOrdered)
results$Gene<-rownames(resOrdered)
results<-results %>% relocate(Gene) %>% filter(padj<0.05, abs(log2FoldChange) >= 1)
results
```

```{r}
vsd <- vst(dds, blind=FALSE)
ntd <- normTransform(dds)
```

```{r}
pcaData <- plotPCA(vsd, intgroup=c("Type"), returnData=TRUE) %>% 
  left_join(sum, by=c("name"="Sample"))
percentVar <- round(100 * attr(pcaData, "percentVar"))


pca<-ggplot(pcaData, aes(PC1, PC2, fill=Type, shape=Type)) +
  geom_point(size=3, alpha=0.9) +
#  geom_text_repel(data=pcaData, aes(x=PC1, y=PC2, fill=Type, label=name)) +
  xlab(paste0("PC1: ",percentVar[1],"% variance")) +
  ylab(paste0("PC2: ",percentVar[2],"% variance")) + 
  coord_fixed() +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  scale_shape_manual(values=c(21,24)) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  scale_fill_viridis_d()

pca
```


```{r}
df<-t(assay(vsd)) %>% as_tibble()
df$Sample<-colnames(vsd)
df$Condition<-vsd$Type
df<-relocate(df,Sample, Condition)
```

```{r}
ddf<-df %>% pivot_longer(cols=3:11521, names_to = c("Gene"), values_to = c("Count"))
ddf
```



```{r}
ggplot(ddf) +
  geom_boxplot(aes(x=Sample, y=Count), cex=0.5) +
  theme(axis.text.x = element_text(angle=45, hjust=1)) +
  facet_grid(.~Condition, scales = "free_x") +
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1, size=5))
ggsave("outputs/1202/expression.jpeg", width=11, height=8.5/2)
```

```{r}
des<-filter(ddf, Gene %in% results$Gene)
sub<-results %>% arrange(-abs(log2FoldChange)) %>% head(n=10)
des<-filter(ddf, Gene %in% sub$Gene)
des <- des %>% left_join(results)

d2 <- des %>% mutate(FoldChange=ifelse(log2FoldChange < 0, "Negative","Positive"))
d2$Sample<-factor(d2$Sample, levels = unique(ddf$Sample))
ggplot() +
  geom_line(data=d2, aes(x=Sample, y=Count, group=Gene, color=FoldChange), alpha=0.5) +
  facet_grid(FoldChange ~ ., scales="free_x") +
  theme(axis.text.x = element_text(angle=45, vjust=0.5)) +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  scale_colour_viridis_d(option="turbo")

```

not a lot of coherent signal across samples. Seems that something else is driving gene expression.


```{r}
depca<-vsd[rownames(vsd) %in% results$Gene,]

pcaData <- plotPCA(depca, intgroup=c("Type"), returnData=TRUE) %>% 
  left_join(sum, by=c("name"="Sample"))
percentVar <- round(100 * attr(pcaData, "percentVar"))


pca<-ggplot(pcaData, aes(PC1, PC2, fill=Type, shape=Type)) +
  geom_point(size=3, alpha=0.9) +
#  geom_text_repel(data=pcaData, aes(x=PC1, y=PC2, fill=Type, label=name)) +
  xlab(paste0("PC1: ",percentVar[1],"% variance")) +
  ylab(paste0("PC2: ",percentVar[2],"% variance")) + 
  coord_fixed() +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  scale_shape_manual(values=c(21,24)) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  scale_fill_viridis_d()

pca
```


Should I log transform data deseq2?

Looking at a significant gene
```{r}

d <- plotCounts(dds, gene="nppb", intgroup="Type", 
                returnData=TRUE)

ggplot(d, aes(x=Type, y=count)) + 
  geom_point(position=position_jitter(w=0.1,h=0)) + 
  scale_y_log10(breaks=c(0,10,20,50,100))

```

It looks like the average expression is different, but lots of overlap, there also tend to be three groups of fish here.  

```{r}
write_csv(results, file="outputs/1202/results05lfc1.csv")
```

```{r}
plotMA(res, ylim=c(-2,2))
```

```{r}
resLFC <- lfcShrink(dds, coef="Type_LDI_vs_HDI", type="apeglm")
```


```{r}
plotMA(resLFC, ylim=c(-2,2))
```

```{r}
plot(res$baseMean+1, -log10(res$pvalue),
     log="x", xlab="mean of normalized counts",
     ylab=expression(-log[10](pvalue)),
     ylim=c(0,15),
     cex=.4, col=rgb(0,0,0,.3))
```
