---
title: "1203-rna-seq-pcas"
output: html_document
date: "2023-07-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
library(DESeq2)
library(viridis)
```



`keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]
```{r}
load("outputs/1201/less-umis.rda")
sum<-read_csv("outputs/1201/sum.csv")
```


```{r}
rowsums<- rowSums(counts(dds)) %>% as_tibble()

ggplot(rowsums) + geom_histogram(aes(x=value))
```


```{r}
ggplot(rowsums %>% filter(value<=10000) %>% filter(value >= 100)) + geom_histogram(aes(x=value)) +
         xlim(0,10000)
```
```{r}
keep <- rowSums(counts(dds)) >= 2500
dds2 <- dds[keep,]

keep2<-rowSums(counts(dds2)) <= 10000
dds2 <- dds2[keep2,]


vsd <- vst(dds2, blind=FALSE)
ntd <- normTransform(dds2)

pcaData <- plotPCA(vsd, intgroup=c("Type"), returnData=TRUE) %>% 
  left_join(sum, by=c("name"="Sample"))
percentVar <- round(100 * attr(pcaData, "percentVar"))


pca<-ggplot(pcaData, aes(PC1, PC2, fill=Type, shape=Type)) +
  geom_point(size=3, alpha=0.9) +
#  geom_text_repel(data=pcaData, aes(x=PC1, y=PC2, fill=Type, label=name)) +
  xlab(paste0("PC1: ",percentVar[1],"% variance")) +
  ylab(paste0("PC2: ",percentVar[2],"% variance")) + 
  coord_fixed() +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  scale_shape_manual(values=c(21,24)) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  scale_fill_viridis_d()

pca

ggsave("outputs/1203/pca.pdf")

```