---
title: "502-local-PCA-MDS"
output: html_document
date: "2023-05-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
library(RColorBrewer)
library(vcfR)
library(adegenet)
```

## Plotting

./run_lostruct.R -i /Users/mac/github/dsm-omics/outputs/500/temp -t snp -s 100 -m 4 -I /Users/mac/github/dsm-omics/outputs/500/sample_info.tsv -j 500

./run_lostruct.R -i /Users/mac/github/dsm-omics/outputs/500/temp -t snp -s 500 -m 4 -I /Users/mac/github/dsm-omics/outputs/500/sample_info.tsv -j 501

./run_lostruct.R -i /Users/mac/github/dsm-omics/outputs/500/temp -t snp -s 200 -m 4 -I /Users/mac/github/dsm-omics/outputs/500/sample_info.tsv -j 502

Making windows 100,200 and 500 bp
```{r}
mds<-read_csv("outputs/500/mds_coords.csv")
#mds<-read_csv("~/github/local_pca/templated/lostruct_results/type_snp_size_200_weights_none_jobid_502/mds_coords.csv")

#make tidy
tidymds<-mds %>% gather(MDS, Value, 3:6)
MDS1<-filter(tidymds, MDS=="MDS1") %>% rename(MDS1=MDS) %>% rename(Value1=Value)
MDS2<-filter(tidymds, MDS=="MDS2") %>% rename(MDS2=MDS) %>% rename(Value2=Value)
MDS3<-filter(tidymds, MDS=="MDS3") %>% rename(MDS3=MDS) %>% rename(Value3=Value)
MDS4<-filter(tidymds, MDS=="MDS4") %>% rename(MDS4=MDS) %>% rename(Value4=Value)
```

```{r}
chromcount<-mds %>% select(chrom) %>% unique()
nb.cols <- nrow(chromcount)
mycolors <- colorRampPalette(brewer.pal(8, "Set1"))(nb.cols)
```

```{r}
p1<-MDS1 %>% mutate(Index=1:n())

out <- boxplot.stats(p1$Value1)$out
out_ind <- which(p1$Value1 %in% c(out))
outliers<-p1[out_ind,]
outliers %>% arrange(Value1)
outliers %>% arrange(-Value1)
```

```{r}
chroms<-p1 %>% group_by(chrom) %>% mutate(Start=min(Index), Stop=max(Index)) %>% select(chrom,Start,Stop) %>% unique() %>% 
  mutate(Position=round((Start+Stop)/2))

#Make enough colors
nb.cols <- nrow(chroms)
mycolors <- colorRampPalette(brewer.pal(8, "Set1"))(nb.cols)


#Hmm.. I should be able to include a bunch of rectangles to offset chroms
ggplot(p1) +
  geom_rect(data=chroms, aes(xmin=Start, xmax=Stop, ymin=min(p1$Value1), ymax=max(p1$Value1)), fill=mycolors, alpha=0.25) +
  geom_point(data=p1, aes(x=Index, y=Value1, color=chrom), alpha=0.75, cex=0.5) +
  geom_point(data=outliers, aes(x=Index, y=Value1), color="black", cex=0.5) +
  theme_bw() +
  scale_x_continuous(breaks=chroms$Position, labels=chroms$chrom) +
  theme(axis.text.x = element_text(angle=45, hjust = 1, face="bold", size=6)) +
  theme(legend.title = element_blank()) +
  theme(panel.grid = element_blank()) +
  theme(legend.position = "none") +
  scale_color_manual(values=mycolors) +
  ylab("MDS1") +
  xlab("Chromosome")
```
```{r}
ggplot(mds, aes(x=MDS1, y=MDS2, color=chrom)) +
  geom_point(alpha=0.9) +
  scale_color_manual(values=mycolors) +
  theme_bw()
```
```{r}
ggplot(mds, aes(x=MDS1, y=MDS3, color=chrom)) +
  geom_point() +
  scale_color_manual(values=mycolors) +
  theme_bw()
```

```{r}
ggplot(mds, aes(x=MDS2, y=MDS3, color=chrom)) +
  geom_point() +
  scale_color_manual(values=mycolors) +
  theme_bw()
```