---
title: "700-dxy"
author: "Mac Campbell"
date: "3/31/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
```

## dxy

This looks to be a good place to start.

Dummy examples.

```{r}
dummy1<-read_tsv("dxy/dummy1.txt")
dummy2<-read_tsv("dxy/dummy2.txt")
dummy3<-read_tsv("dxy/dummy3.txt")

dummy1
dummy2
dummy3
```
script uses "knownEM"   for dxy calculation, 
`Explicitly: 0.5 * (1-0.5) + (0.5 * (1-0.5)) = .25 + .25 = 0.5`
`Explicitly: (0.4 * (1-0.4) + (0.4 * (1-0.4)) = .24 + .24 =0.48`

```{sh, eval=FALSE}
./getDxy.pl --pop1maf dummy1.txt --pop2maf dummy1.txt --minInd 5 > dummy1-dummy1.tsv #same allele freqs
./getDxy.pl --pop1maf dummy1.txt --pop2maf dummy2.txt --minInd 5 > dummy1-dummy2.tsv #opposite allele freqs
./getDxy.pl --pop1maf dummy1.txt --pop2maf dummy3.txt --minInd 5 > dummy1-dummy3.tsv # allele freqs constant at 0.5 in dummy3

```

```{r}
d1d1<-read_tsv("dxy/dummy1-dummy1.tsv")
d1d2<-read_tsv("dxy/dummy1-dummy2.tsv")
d1d3<-read_tsv("dxy/dummy1-dummy3.tsv")
d1d4<-read_tsv("dxy/dummy1-dummy4.tsv")
d1d5<-read_tsv("dxy/dummy1-dummy5.tsv")
d1d6<-read_tsv("dxy/dummy1-dummy6.tsv")

```


```{r}
ggplot(d1d1) +
  geom_point(aes(x=Dxy, y=position)) +
  theme_classic() +
  ylab("Allele Frequencies") +
  ggtitle("Dxy when allele frequencies are the same\n") +
  theme(plot.title = element_text(hjust=0.5))
```

Maximal dxy is 0.5 when the allele frequencies are 0.5, maximal diversity?

```{r}
d1d2df<-d1d2 %>% mutate(position2=1-position) %>% select(chromo,Dxy,position,position2) %>% 
  rename(Freq1=position, Freq2=position2) %>% gather(key=Position, value=AlleleFreq, 3:4)
```

```{r}
ggplot(d1d2df, aes(x=Dxy, y=AlleleFreq, color=AlleleFreq)) +
  geom_point() +
  theme_classic() +
  ylab("Allele Frequencies") +
  ggtitle("Dxy when allele frequencies are oppositional\n") +
  theme(plot.title = element_text(hjust=0.5)) +
  facet_grid(Position ~ .)
```

dxy is maximal when major allele freqs are 1,0 or 0,1 and is = 1.


Varying allele freqs

```{r}
d3<-d1d3 %>% mutate(AF=0.5)
d4<-d1d4 %>% mutate(AF=0.4)
d5<-d1d5 %>% mutate(AF=0.3)
d6<-d1d6 %>% mutate(AF=0.6)

combo<-bind_rows(d3,d4,d5,d6)
combo$AF<-as.factor(combo$AF)
```

```{r}
ggplot(combo) +
  geom_point(aes(x=position, y=Dxy, color=AF)) +
  xlab("AF pop 2") +
  theme_bw()

```

If AF is = 0.5, Dxy = 0.5, if < 0.5 or > 0.5 can get Dxy to change

## Steps

Matt seyz:    
_1_ Use ANGSD to score SNPs, p-value cutoff as normal, minQ, minmapQ, etc. etc.     
_2_ Make a text file with the IDs of the SNPs you want to compare between populations. I scored SNPs separately for Sashin steelhead and rainbows in step one because I assumed the rainbows to have fuck all genetic variation and I didn’t want alleles that were fixed in the rainbows and polymorphic in the steelhead to get filtered out because of -minInd or -minMaf filtering. If you’ve already done this, i.e., you’ve combined all your delta smelts together into one ANGSD file then you can forgo this step.     
_3_ Here’s the ANGSD command I used: ./angsd -b sashin_RT_bams -ref RBT_fullGenome.fasta -out rainbows_3 -GL 1 -minQ 20 -minMapQ 20 -doMajorMinor 1 -doMaf 3 -minMaf 0.05 -sites ~/Downloads/angsd/misc/intersect.txt -nThreads 16 
_4_ I repeated this for the steelhead so I had two maf.gz files one for steelhead and one for rainbows. I then gunziped the maf files.
_5_ Run through perl…might be an idea to run “head name of maf file” first so you can make sure all the necessary colums are there. It should be chromo position major minor ref knownEM unknownEM nInd ./per getDxy.pl –pop1maf ~/Downloads/angsd/steelhead3.mafs –pop2maf ~/Downloads/angsd/rainbows3.mafs –minInd 12 > dxy_sashin_out.txt  
 
A tutorial exists: https://github.com/mfumagalli/ngsTools/blob/master/TUTORIAL.md    

_1_ We first compute the sample allele frequency likelihoods using ANGSD.    
_2_ Need to get the subset of overlapping sites (unfiltered for both populations)     
_3_ We then compute the sample allele frequency likelihoods only for the overlapping (valid) sites.    

_1_ Getting bamlists together.

```{r}
kept96<-read_tsv("meta/kept96.tsv")

kept96 %>% group_by(CrossType) %>% summarize(Count=n())
```

91 samples split between HDI and LDI.

```{r}
write_tsv(kept96 %>% select(String), col_names = FALSE, file = "bamlists/test91.bamlist")

write_tsv(kept96 %>% filter(CrossType=="HDI") %>% select(String), col_names = FALSE, file = "bamlists/testHDI.bamlist")
write_tsv(kept96 %>% filter(CrossType=="LDI") %>% select(String), col_names = FALSE, file = "bamlists/testLDI.bamlist")
```

using one chrom to test 

_1_ Getting SNPS    

Can fold with -doSaf 1 -anc $REF

```{sh, eval=FALSE}
srun -p bigmemm -t 12:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -nThreads 6 \
  -minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
  -doGeno 2 -doPost 1 -postCutoff 0.95 -doPlink 2 -ref $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -bam  bamlists/testHDI.bamlist -minInd 38  -doCounts 1  \
  -r NC_061060.1 -out outputs/700/testHDI > outputs/700/testHDI.stdout 2> outputs/700/testHDI.stderr &

srun -p bigmemm -t 12:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -nThreads 6 \
  -minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
  -doGeno 2 -doPost 1 -postCutoff 0.95 -doPlink 2 -ref $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -bam  bamlists/testLDI.bamlist -minInd 44 -doCounts 1  \
  -r NC_061060.1 -out outputs/700/testLDI > outputs/700/testLDI.stdout 2> outputs/700/testLDI.stderr &

srun -p bigmemm -t 1-12:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -nThreads 6 \
  -minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
  -doGeno 2 -doPost 1 -postCutoff 0.95 -doPlink 2 -ref $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -bam  bamlists/test91.bamlist -minInd 82  -doCounts 1 \
   -out outputs/700/test91 > outputs/700/test91.stdout 2> outputs/700/test91.stderr &

```




_2_ Compute intersect

-fold 1 should be passed to realSFS, bc folded spectra

```{sh, eval=FALSE}
$HOME/angsd/misc/realSFS print outputs/700/testHDI.saf.idx outputs/700/testLDI.saf.idx | cut -f 1-2 > outputs/700/intersect.txt

$HOME/angsd/angsd sites index outputs/700/intersect.txt

NSITES=`wc -l outputs/700/intersect.txt | cut -f 1 -d " "`
echo $NSITES
```
16925 sites

_3_ Compute the sample allele frequency likelihoods only for the overlapping (valid) sites.

```{sh, eval=FALSE}
srun -p bigmemm -t 12:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -nThreads 6 \
  -minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
  -doGeno 2 -doPost 1 -postCutoff 0.95 -doPlink 2  -ref  $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -bam  bamlists/testHDI.bamlist -minInd 38  -doCounts 1  \
  -r NC_061060.1 -sites outputs/700/intersect.txt -out outputs/700/testHDI-int > outputs/700/testHDI-int.stdout 2> outputs/700/testHDI-int.stderr &

srun -p bigmemm -t 12:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -nThreads 6 \
  -minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
  -doGeno 2 -doPost 1 -postCutoff 0.95 -doPlink 2  -ref  $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -bam  bamlists/testLDI.bamlist -minInd 44 -doCounts 1  \
  -r NC_061060.1 -sites outputs/700/intersect.txt -out outputs/700/testLDI-int > outputs/700/testLDI-int.stdout 2> outputs/700/testLDI-int.stderr &
```


_4_ Now run get dxy on each .saf

 It should be chromo position major minor ref knownEM unknownEM nInd      
 ./per getDxy.pl –pop1maf ~/Downloads/angsd/steelhead3.mafs –pop2maf ~/Downloads/angsd/rainbows3.mafs –minInd 12 > dxy_sashin_out.txt  
```{sh, eval=FALSE}
../../dxy/getDxy.pl -pop1maf testHDI-int.mafs -pop2maf testLDI-int.mafs -minInd 40 > dxy.txt
```


```{r}
dxy<-read_tsv("outputs/700/dxy.txt")
```

```{r}
ggplot(dxy) +
  geom_point(aes(x=position, y=Dxy), pch=21, alpha=0.5, fill="grey") +
  theme(panel.grid=element_blank())
```

As boxplot     

```{r}
ggplot(dxy) + 
  geom_boxplot(aes(x=chromo,y=Dxy))
```

```{r}
boxplot.stats(dxy$Dxy)$out
```

Now for all chroms: using doSaf1

```{sh, eval=FALSE}
srun -p bigmemh -t 3-12:00:00 --mail-type=ALL --mem=32G --nodes=1 $HOME/angsd/angsd -nThreads 6 \
  -minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
  -doGeno 2 -doPost 1 -postCutoff 0.95 -doPlink 2 -doSaf 1 -anc $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -bam  bamlists/testHDI.bamlist -minInd 38  -doCounts 1  \
  -out /home/maccamp/dsm-omics/outputs/700/all-chroms-HDI > /home/maccamp/dsm-omics/outputs/700/testHDI.stdout 2> /home/maccamp/dsm-omics/outputs/700/testHDI.stderr &

srun -p bigmemh -t 3-12:00:00 --mail-type=ALL --mem=32G --nodes=1 $HOME/angsd/angsd -nThreads 6 \
  -minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
  -doGeno 2 -doPost 1 -postCutoff 0.95 -doPlink 2 -doSaf 1 -anc $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -bam  bamlists/testLDI.bamlist -minInd 44 -doCounts 1  \
  -out /home/maccamp/dsm-omics/outputs/700/all-chroms-testLDI >/home/maccamp/dsm-omics/outputs/700/testLDI.stdout 2> /home/maccamp/dsm-omics/outputs/700/testLDI.stderr &

```

Find intersect:    

```{sh, eval=FALSE}
$HOME/angsd/misc/realSFS print outputs/700/all-chroms-HDI.saf.idx outputs/700/all-chroms-testLDI.saf.idx | cut -f 1-2 > outputs/700/all-chroms-intersect.txt

$HOME/angsd/angsd sites index outputs/700/all-chroms-intersect.txt

NSITES=`wc -l outputs/700/all-chroms-intersect.txt | cut -f 1 -d " "`
echo $NSITES
```

641913 sites, redoing results in 641892 sites!!!!!

Compute for overlapping sites:


```{sh, eval=FALSE}
srun -p bigmemm -t 3-12:00:00 --mail-type=ALL --mem=32G --nodes=1 $HOME/angsd/angsd -nThreads 6 \
  -minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
  -doGeno 2 -doPost 1 -postCutoff 0.95 -doPlink 2 -doSaf 1 -anc $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -bam  bamlists/testHDI.bamlist -minInd 38  -doCounts 1 -sites outputs/700/all-chroms-intersect.txt \
  -out /home/maccamp/dsm-omics/outputs/700/all-chroms-HDI-intersect > /home/maccamp/dsm-omics/outputs/700/testHDI.stdout 2> /home/maccamp/dsm-omics/outputs/700/testHDI.stderr &

srun -p bigmemh -t 3-12:00:00 --mail-type=ALL --mem=32G --nodes=1 $HOME/angsd/angsd -nThreads 6 \
  -minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
  -doGeno 2 -doPost 1 -postCutoff 0.95 -doPlink 2 -doSaf 1 -anc $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -bam  bamlists/testLDI.bamlist -minInd 44 -doCounts 1  -sites outputs/700/all-chroms-intersect.txt\
  -out /home/maccamp/dsm-omics/outputs/700/all-chroms-LDI-intersect >/home/maccamp/dsm-omics/outputs/700/testLDI.stdout 2> /home/maccamp/dsm-omics/outputs/700/testLDI.stderr &

```

Compute dxy, it outputs/700

```{sh, eval=FALSE}
gunzip all-chroms*intersect.mafs.gz
../../dxy/getDxy.pl -pop1maf all-chroms-HDI-intersect.mafs -pop2maf all-chroms-LDI-intersect.mafs -minInd 35 > all-chroms-dxy.txt
```
Some more ideas:

Compute LD decay, sliding window Fsts. Phase with beagle or shapeit, haplotype statistics within HDI and between HDI and LDI with rehh?

```{r}
ddxy<-read_tsv("outputs/700/all-chroms-dxy-2min.txt") 
chromo<-ddxy[str_starts(ddxy$chromo, "NC"),]
```
202,446 positions with getDxy.pl -minInd 35
180,901 positions with getDxy.pl -minInd 40
```{r}
outs<-boxplot.stats(chromo$Dxy)$out

dfouts<-chromo %>% filter(Dxy %in% outs)
```

```{r}
ggplot(chromo) +
  geom_point(aes(x=position, y=Dxy), pch=21, alpha=0.5, fill="grey", cex=1) +
  geom_point(data=dfouts, aes(x=position, y=Dxy), pch=21, alpha=0.75, fill="skyblue",cex=2) +
  theme(panel.grid=element_blank()) +
  facet_wrap(.~chromo, scales = "free_x", ncol = 6)

ggsave("outputs/700/dxy.jpeg", width=15, height=12)
```

redoing, 'cause weird.


Hmm, my mafs file has the wrong columns
head all-chroms-LDI-intersect.mafs 
chromo	position	major	minor	anc	knownEM	pK-EM	nInd

../../dxy/getDxy-two-mins.pl -pop1maf all-chroms-HDI-intersect.mafs -pop2maf all-chroms-LDI-intersect.mafs -minInd 35 -minInd2 40 > all-chroms-dxy-2min.txt


Matt:: ./angsd -b sashin_RT_bams -ref RBT_fullGenome.fasta -out rainbows_3 -GL 1 -minQ 20 -minMapQ 20 -doMajorMinor 1 -doMaf 3 -minMaf 0.05 -sites ~/Downloads/angsd/misc/intersect.txt -nThreads 16 
What about like this?

`(base) maccamp@farm:~/dsm-omics/outputs/700$ head -n 1000 all-chroms-intersect.txt > all-chroms-intersect-1000.txt`
`$HOME/angsd/angsd sites index all-chroms-intersect-1000.txt`

```{sh, eval=FALSE}
srun -p high -t 2:00:00 --mail-type=ALL --mem=16G --nodes=1 $HOME/angsd/angsd -nThreads 6 \
  -minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
  -ref $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -bam  bamlists/testHDI.bamlist -minInd 38 -r NC_061060.1 -sites outputs/700/all-chroms-intersect-100.txt \
  -out /home/maccamp/dsm-omics/outputs/700/hdi-100-basic > /home/maccamp/dsm-omics/outputs/700/hdi-100-basic.stdout 2> /home/maccamp/dsm-omics/outputs/700/hdi-100-basic.stderr &

srun -p high -t 2:00:00 --mail-type=ALL --mem=16G --nodes=1 $HOME/angsd/angsd -nThreads 6 \
  -minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
  -ref $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -bam  bamlists/testLDI.bamlist -minInd 44 -r NC_061060.1 -sites outputs/700/all-chroms-intersect-100.txt \
  -out /home/maccamp/dsm-omics/outputs/700/ldi-100-basic >/home/maccamp/dsm-omics/outputs/700/ldi-100-basic.stdout 2> /home/maccamp/dsm-omics/outputs/700/ldi-100-basic.stderr &

```

With basic, I have: chromo	position	major	minor	ref	knownEM	pK-EM	nInd
Not,                chromo	position	major	minor	ref	knownEM	unknownEM	nInd

../../dxy/getDxy-two-mins.pl -pop1maf hdi-100-basic.mafs -pop2maf ldi-100-basic.mafs -minInd 35 -minInd2 40 

```{sh, eval=FALSE}
srun -p high -t 3-12:00:00 --mail-type=ALL --mem=16G --nodes=1 $HOME/angsd/angsd -nThreads 6 \
  -minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
  -ref $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -bam  bamlists/testHDI.bamlist -minInd 38 -sites outputs/700/all-chroms-intersect.txt \
  -out /home/maccamp/dsm-omics/outputs/700/hdi-basic > /home/maccamp/dsm-omics/outputs/700/hdi-basic.stdout 2> /home/maccamp/dsm-omics/outputs/700/hdi-basic.stderr &

srun -p high -t 3-12:00:00 --mail-type=ALL --mem=16G --nodes=1 $HOME/angsd/angsd -nThreads 6 \
  -minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
  -ref $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -bam  bamlists/testLDI.bamlist -minInd 44 -sites outputs/700/all-chroms-intersect.txt \
  -out /home/maccamp/dsm-omics/outputs/700/ldi-basic >/home/maccamp/dsm-omics/outputs/700/ldi-basic.stdout 2> /home/maccamp/dsm-omics/outputs/700/ldi-basic.stderr &

```

hdi-basic/ldi-basic ran to completion.

(base) maccamp@farm:~/dsm-omics/outputs/700$ head hdi-basic.mafs 
chromo	position	major	minor	ref	knownEM	pK-EM	nInd
NC_061060.1	1155	T	A	T	0.349508	0.000000e+00	42
NC_061060.1	17087	A	T	A	0.325057	0.000000e+00	42

(base) maccamp@farm:~/dsm-omics/outputs/700$ wc -l ldi-basic.mafs 
641887 ldi-basic.mafs
(base) maccamp@farm:~/dsm-omics/outputs/700$ wc -l hdi-basic.mafs 
641883 hdi-basic.mafs
Ahhh.... We don't have the same number of lines in the files, so getDxy gives us funny results!!!!!!!!!!!!!!!!!!

../../dxy/getDxy-two-mins.pl -pop1maf hdi-basic.mafs -pop2maf ldi-basic.mafs -minInd 35 -minInd2 40 > basic.mafs

```{r}
ddxy<-read_tsv("outputs/700/basic.mafs") 
chromo<-ddxy[str_starts(ddxy$chromo, "NC"),]

outs<-boxplot.stats(chromo$Dxy)$out

dfouts<-chromo %>% filter(Dxy %in% outs)
```

```{r}
ggplot(chromo) +
  geom_point(aes(x=position, y=Dxy), pch=21, alpha=0.5, fill="grey", cex=1) +
  geom_point(data=dfouts, aes(x=position, y=Dxy), pch=21, alpha=0.75, fill="skyblue",cex=2) +
  theme(panel.grid=element_blank()) +
  facet_wrap(.~chromo, scales = "free_x", ncol = 6)

ggsave("outputs/700/dxybasic.jpeg", width=15, height=12)
```



#### manual calc
first, some interesting sites

```{r}
cs<-c("NC_061062.1","NC_061064.1","NC_061065.1","NC_061065.1")
ps<-c(12081162,2535255,13099447,13101117)

int<-cbind(cs,ps) %>% as_tibble() %>% rename(chromo=cs, position=ps)
int$position<-as.numeric(int$position)
int
```


```{r}
hi<-read_tsv("outputs/700/hdi-basic.mafs") %>% rename(MajorHi=major, MinorHi=minor, EmHi=knownEM, HiInd=nInd) %>% select(-`pK-EM`)

lo<-read_tsv("outputs/700/ldi-basic.mafs") %>% rename(MajorLo=major, MinorLo=minor, EmLo=knownEM, LoInd=nInd) %>% select(-`pK-EM`)

hi
```

```{r}
inner<-inner_join(hi,lo) %>% filter(MajorHi!=MajorLo) 
left_join(int, inner)
```

Make the same
```{r}
mafs<-inner_join(hi,lo ) %>% mutate(NewLo=ifelse(MajorHi != MajorLo, 1-EmLo, EmLo)) %>%
  mutate(Dxy= (EmHi * (1-NewLo)) + (NewLo * (1-EmHi)) ) %>% 
  mutate(Abs=abs(EmHi-NewLo)) %>%
  filter(HiInd > 35) %>% filter(LoInd > 40)
mafs
```

```{r}
left_join(int,mafs)
```

From script

```{r}
ddxy
```

Creating figure.....

```{r}
chrom<-mafs[str_starts(mafs$chromo, "NC"),]

out<-boxplot.stats(chrom$Dxy)

dfout<-chrom %>% filter(Dxy %in% out)
```

```{r}
ggplot(chrom) +
  geom_point(aes(x=position, y=Dxy), pch=21, alpha=0.5, fill="grey", cex=1) +
  geom_point(data=dfout, aes(x=position, y=Dxy), pch=21, alpha=0.75, fill="skyblue",cex=2) +
  theme(panel.grid=element_blank()) +
  facet_wrap(.~chromo, scales = "free_x", ncol = 6) +
  ylim(0,1)

ggsave("outputs/700/dxybasic-coded-calc.jpeg", width=15, height=12)
```


```{r}
mafs %>% arrange(-Dxy)
```



### Another option
-doMaf 3 -ref (switching back to anc)

```{sh, eval=FALSE}
srun -p high -t 2:00:00 --mail-type=ALL --mem=16G --nodes=1 $HOME/angsd/angsd -nThreads 6 \
  -minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 3 -SNP_pval 1e-6 \
  -doGeno 2 -doPost 1 -postCutoff 0.95 -doPlink 2 -doSaf 1 -anc $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -bam  bamlists/testHDI.bamlist -minInd 38  -doCounts 1 -r NC_061060.1 -sites outputs/700/all-chroms-intersect-1000.txt \
  -out /home/maccamp/dsm-omics/outputs/700/hdi-1000 > /home/maccamp/dsm-omics/outputs/700/hdi-1000.stdout 2> /home/maccamp/dsm-omics/outputs/700/hdi-1000.stderr &

srun -p high -t 2:00:00 --mail-type=ALL --mem=16G --nodes=1 $HOME/angsd/angsd -nThreads 6 \
  -minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 3 -SNP_pval 1e-6 \
  -doGeno 2 -doPost 1 -postCutoff 0.95 -doPlink 2 -doSaf 1 -anc $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -bam  bamlists/testLDI.bamlist -minInd 44 -doCounts 1 -r NC_061060.1 -sites outputs/700/all-chroms-intersect-1000.txt \
  -out /home/maccamp/dsm-omics/outputs/700/ldi-1000 >/home/maccamp/dsm-omics/outputs/700/ldi-1000.stdout 2> /home/maccamp/dsm-omics/outputs/700/ldi-1000.stderr &

```
(base) maccamp@farm:~/dsm-omics/outputs/700$ head ldi-1000.mafs 
chromo	position	major	minor	anc	knownEM	unknownEM	pK-EM	pu-EM	nInd
NC_061060.1	1155	T	A	T	0.286183	0.286183	0.000000e+00	0.000000e+00	45
NC_061060.1	17087	A	T	A	0.459444	0.459444	0.000000e+00	0.000000e+00	48
NC_061060.1	17129	C	T	C	0.058146	0.058146	0.000000e+00	0.000000e+00	48

abcFreq.cpp] You have selected filters for maf/lrt
If you have selected more than one MAF estimator we will choose in following order
	1. knownminor EM
	2. unknownminor EM
	3. Posterior maf
	-> Must supply -anc for polarizing the spectrum

../../dxy/getDxy.pl-two-mins.pl -pop1maf all-chroms-HDI-intersect.mafs -pop2maf all-chroms-LDI-intersect.mafs -minInd 35 -minInd 40 > all-chroms-dxy-2min.txt

