---
title: "701-Fst"
author: "Mac Campbell"
date: "6/30/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```


```{r}
library(tidyverse)
```

## Fst

Fst looks to be a good place to start.    

```{sh, eval=FALSE}
srun -p bigmemh -t 12:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -b bamlists/testHDI.bamlist -anc $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -ref $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -r NC_061060.1:1-100000 \
  -uniqueOnly 1 -remove_bads 1 -only_proper_pairs 1 -baq 2 -GL 1  -doMaf 1 -doMajorMinor 1 \
  -minMapQ 20 -minQ 20 -doSaf 1 -nThreads 8  \
  -minInd 38 -nind 42 -out outputs/701/hdi > outputs/701/hdi.stdout 2> outputs/701/hdi.stderr &
  
srun -p bigmemh -t 12:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -b bamlists/testLDI.bamlist -anc $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -ref $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -r NC_061060.1:1-100000 \
  -uniqueOnly 1 -remove_bads 1 -only_proper_pairs 1 -baq 2 -GL 1  -doMaf 1 -doMajorMinor 1 \
  -minMapQ 20 -minQ 20 -doSaf 1 -nThreads 8  \
  -minInd 44 -nind 49 -out outputs/701/ldi > outputs/701/ldi.stdout 2> outputs/701/ldi.stderr &
  
```

Commands like this:

```{sh, eval=FALSE}
realSFS outputs/701/hdi.saf.idx >  outputs/701/hdi.sfs
realSFS outputs/701/ldi.saf.idx >  outputs/701/ldi.sfs
realSFS outputs/701/hdi.saf.idx outputs/701/ldi.saf.idx > outputs/701/hdi-ldi.2dsfs
realSFS fst index  outputs/701/hdi.saf.idx  outputs/701/ldi.saf.idx -sfs outputs/701/hdi-ldi.2dsfs -fstout outputs/701/hdi-ldi
realSFS fst stats outputs/701/hdi-ldi.fst.idx > outputs/701/hdi-ldi.fst.stats
realSFS fst stats2  outputs/701/hdi-ldi.fst.idx -win 50000 -step 10000 >  outputs/701/sliding-window-50k-10k
```

If it works, we can repeat for all chroms together

(base) maccamp@farm:~/dsm-omics$ cat outputs/701/hdi-ldi.fst.stats 
0.005856	0.028124

(base) maccamp@farm:~/dsm-omics$ cat outputs/701/sliding-window-50k-10k 
region	chr	midPos	Nsites
(292,42398)(13968,59999)(10000,60000)	NC_061060.1	35000	42108	0.021744
(3148,52272)(20000,69999)(20000,70000)	NC_061060.1	45000	49126	0.024752
(12515,62272)(30000,79999)(30000,80000)	NC_061060.1	55000	49759	0.030770
(22419,72101)(40000,89999)(40000,90000)	NC_061060.1	65000	49684	0.027812
(32406,82046)(50000,99999)(50000,100000)	NC_061060.1	75000	49642	0.028658

Looks fine. Trying with all the chroms. (but didn't specify, do'h)

```{sh, eval=FALSE}
srun -p bigmemh -t 3-12:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -b bamlists/testHDI.bamlist -anc $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -ref $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -uniqueOnly 1 -remove_bads 1 -only_proper_pairs 1 -baq 2 -GL 1  -doMaf 1 -doMajorMinor 1 \
  -minMapQ 20 -minQ 20 -doSaf 1 -nThreads 8  \
  -minInd 38 -nind 42 -out outputs/701/hdi > outputs/701/hdi.stdout 2> outputs/701/hdi.stderr &
  
srun -p bigmemh -t 3-12:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -b bamlists/testLDI.bamlist -anc $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -ref $HOME/genomes/GCF021917145.1/GCF_021917145.1_fHypTra1_genomic.fna \
  -uniqueOnly 1 -remove_bads 1 -only_proper_pairs 1 -baq 2 -GL 1  -doMaf 1 -doMajorMinor 1 \
  -minMapQ 20 -minQ 20 -doSaf 1 -nThreads 8  \
  -minInd 44 -nind 49 -out outputs/701/ldi > outputs/701/ldi.stdout 2> outputs/701/ldi.stderr &
  
```

Completed runs.... 

Should set up a script to run realSFS, see 701.1-sfs.sh, can execute with srun.
(base) maccamp@farm:~/dsm-omics$ srun -p high -t 2:00:00 --nodes=1 bash 701.1-sfs.sh > outputs/701/sfs.stdout 2> outputs/701/sfs.stderr &

You know, I could do per chromosome fst, this wants a lot of memory!

 srun -p bigmemh -t 1-2:00:00 --nodes=1 --mem=32G  bash 701.1-sfs.sh > outputs/701/sfs.stdout 2> outputs/701/sfs.stderr &

Only finished 5 chroms in 2 hrs, 